Introduction to Moltres: an Application for Simulation of Molten Salt Reactors

### 2017-07-27 Moltres.tex
Introduce comparison with MSRE, 3d results, scaling study.

\documentclass{article}
\setlength{\parindent}{0pt}
\setlength{\parskip}{2ex plus 0.5ex minus 0.2ex}
\usepackage[margin=1in]{geometry}
\renewcommand{\topfraction}{0.9}
\renewcommand{\bottomfraction}{0.8}
\setcounter{topnumber}{2}
\setcounter{bottomnumber}{2}
\setcounter{totalnumber}{4}
\renewcommand{\textfraction}{0.07}
\renewcommand{\floatpagefraction}{0.7}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{placeins}
\usepackage[T1]{fontenc}
\usepackage{gensymb}
\usepackage[utf8]{inputenc}
\usepackage{caption}
\usepackage[export]{adjustbox}
\graphicspath{{./figures/}}
% hyperref usually has to go last
\usepackage[hidelinks]{hyperref}
% but glossaries behaves best if after hyperref
\usepackage[acronym,toc]{glossaries}
\include{acros}
\makeglossaries
% cleveref only behaves if after hyperref & glossaries
\usepackage{cleveref}
\usepackage{minted}

@@

\newcommand{\code}[1]{\texttt{#1}}

@@

Group constants are generated by the modeler with either Serpent
\cite{leppanen_serpent_2015} or Scale \cite{dehart_reactor_2011}. Group constant
temperature dependence is implemented via interpolation tables, which must be
constructed separately for fuel and moderator regions.

@@

\begin{figure}
  \centering
  \includegraphics{geometry.eps}
  \label{fig:geom}
  \caption{A sketch of the \gls{MSR} model geometry}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics{auto_diff_rho_group1.eps}
        \caption{The group 1 flux in this 2-D cylindrical axisymmetric model
        has the anticipated magnitude and canonical cosine shape ($r=0$ is center of core). }
  \label{fig:group1}
\end{figure}

\begin{figure}
  \centering
  \includegraphics{auto_diff_rho_group2.eps}
        \caption{The group 2 flux in this 2-D cylindrical axisymmetric model
        has the anticipated magnitude and canonical cosine shape ($r=0$ is center of core). }
  \label{fig:group2}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics{radial_group_comparison.eps}
  \caption{The thermal and fast flux profiles are compared at the core mid-plane
    ($z=H/2$) in this 2-D cylindrical axisymmetric model ($r=0$ is radial center
    of core). }
  \label{fig:flux_comparison}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics{auto_diff_rho_temp.eps}
        \caption{The reactor core temperature peaks near the reactor outlet in
          this 2-D axisymmetric model because of fuel advection ($r=0$ is center
          of core).}
  \label{fig:temp}
\end{figure}

@@

% Fix me! Precursor concentrations have goofy scaling
\begin{figure}
  \centering
  \includegraphics{auto_diff_rho_pre1.eps}
        \caption{The concentration of the group of longest lived precursors
        ($\lambda = 1.24\cdot 10^{-2} s^{-1}$) peaks near the reactor outlet
        in this 2-D axisymmetric model ($r=0$ is center of core).}
  \label{fig:pre1}
\end{figure}

@@

% Fix me! Precursor concentrations have goofy scaling
\begin{figure}
  \centering
  \includegraphics{auto_diff_rho_pre6.eps}
        \caption{The concentration of the group of shortest lived precursors
        ($\lambda = 3.07 s^{-1}$) peaks near the reactor center
        in this 2-D axisymmetric model ($r=0$ is center of core).}
  \label{fig:pre6}
\end{figure}

>>>>

\documentclass{article}
\setlength{\parindent}{0pt}
\setlength{\parskip}{2ex plus 0.5ex minus 0.2ex}
\usepackage[margin=1in]{geometry}
\renewcommand{\topfraction}{0.9}
\renewcommand{\bottomfraction}{0.8}
\setcounter{topnumber}{2}
\setcounter{bottomnumber}{2}
\setcounter{totalnumber}{4}
\renewcommand{\textfraction}{0.07}
\renewcommand{\floatpagefraction}{0.7}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{placeins}
\usepackage[T1]{fontenc}
\usepackage{gensymb}
\usepackage[utf8]{inputenc}
\usepackage{caption}
\usepackage[export]{adjustbox}
\graphicspath{{./figures/}}
% hyperref usually has to go last
\usepackage[hidelinks]{hyperref}
% but glossaries behaves best if after hyperref
\usepackage[acronym,toc]{glossaries}
\include{acros}
\makeglossaries
% cleveref only behaves if after hyperref & glossaries
\usepackage{cleveref}
\usepackage{minted}
\usepackage{ifthen}
%% \usepackage{listings}  % Allows code printing
%% \definecolor{codegreen}{rgb}{0,0.6,0}
%% \definecolor{codegray}{rgb}{0.5,0.5,0.5}
%% \definecolor{codepurple}{rgb}{0.58,0,0.82}
%% \definecolor{backcolour}{rgb}{0.95,0.95,0.92}
%% \lstdefinestyle{mystyle}{
%%     backgroundcolor=\color{backcolour},
%%     commentstyle=\color{codegreen},
%%     keywordstyle=\color{magenta},
%%     numberstyle=\tiny\color{codegray},
%%     stringstyle=\color{codepurple},
%%     basicstyle=\footnotesize,
%%     breakatwhitespace=false,
%%     breaklines=true,
%%     captionpos=b,
%%     keepspaces=true,
%%     numbers=left,
%%     numbersep=5pt,
%%     showspaces=false,
%%     showstringspaces=false,
%%     showtabs=false,
%%     tabsize=2
%% }
%% \lstset{style=mystyle}

@@

\newcommand{\code}[1]{\texttt{#1}}
\makeatletter
\def\maxwidth#1{\ifdim\Gin@nat@width>#1 #1\else\Gin@nat@width\fi}
\makeatother

@@

Group constants are generated by the modeler with either Serpent
\cite{leppanen_serpent_2015} or SCALE \cite{dehart_reactor_2011}. Group constant
temperature dependence is implemented via interpolation tables, which must be
constructed separately for fuel and moderator regions. For this report,
SCALE-generated group constants were used. To generate the group constants, an
infinite square pitch lattice of cylindrical fuel channels surrounded by
graphite was used, maintaining a fuel fraction of .225 to be consistent with the
\gls{MSRE}. Subsequently, a critical buckling calculation was applied. The SCALE
input files used for generating the group constants can be found in the
\code{io/msre\_conc\_cuboid\_lattice} directory of the
\url{github.com/arfc/scale_io} repository.

@@

\begin{figure}[htpb]
  \centering
  \includegraphics{geometry.eps}
  \label{fig:geom}
  \caption{A sketch of the \gls{MSR} model geometry}
\end{figure}

@@

\begin{figure}[htpb]
  \centering
  \includegraphics{2d_gamma_heating_group1.eps}
        \caption{The group 1 flux in this 2-D cylindrical axisymmetric model
        has the anticipated magnitude and canonical cosine shape ($r=0$ is center of core). }
  \label{fig:group1}
\end{figure}

\begin{figure}[htpb]
  \centering
  \includegraphics{2d_gamma_heating_group2.eps}
        \caption{The group 2 flux in this 2-D cylindrical axisymmetric model
        has the anticipated magnitude and canonical cosine shape ($r=0$ is center of core). }
  \label{fig:group2}
\end{figure}

@@

\begin{figure}[htpb]
  \centering
  \includegraphics{radial_group_comparison.eps}
  \caption{The thermal and fast flux profiles are compared at the core mid-plane
    ($z=H/2$) in this 2-D cylindrical axisymmetric model ($r=0$ is radial center
    of core). }
  \label{fig:flux_comparison}
\end{figure}

@@

\begin{figure}[htpb]
  \centering
  \includegraphics{2d_gamma_heating_temp.eps}
        \caption{The reactor core temperature peaks near the reactor outlet in
          this 2-D axisymmetric model because of fuel advection ($r=0$ is center
          of core). Because of heating by gammas and other radiation the
          moderator regions are hotter than the fuel, consistent with
          observations of the \gls{MSRE}}
  \label{fig:temp}
\end{figure}

@@

% Fix me! Precursor concentrations have goofy scaling
\begin{figure}[htpb]
  \centering
  \includegraphics{2d_gamma_heating_pre1.eps}
        \caption{The concentration of the group of longest lived precursors
        ($\lambda = 1.24\cdot 10^{-2} s^{-1}$) peaks near the reactor outlet
        in this 2-D axisymmetric model ($r=0$ is center of core).}
  \label{fig:pre1}
\end{figure}

@@

% Fix me! Precursor concentrations have goofy scaling
\begin{figure}[htpb]
  \centering
  \includegraphics{2d_gamma_heating_pre6.eps}
        \caption{The concentration of the group of shortest lived precursors
        ($\lambda = 3.07 s^{-1}$) peaks near the reactor center
        in this 2-D axisymmetric model ($r=0$ is center of core).}
  \label{fig:pre6}
\end{figure}

\subsection{3D}

\begin{figure}[htpb]
  \centering
  \includegraphics{3d_gamma_heating_group1.eps}
        \caption{Fast flux for 3D \gls{MSRE}-like model. Magnitude and shape in
          good agreement with 2D axisymmetric model (see \cref{fig:group1})}
  \label{fig:3d_group1}
\end{figure}

\begin{figure}[htpb]
  \centering
  \includegraphics{3d_gamma_heating_temp.eps}
        \caption{Temperature for 3D \gls{MSRE}-like model. Magnitude and shape in
          good agreement with 2D axisymmetric model (see \cref{fig:temp})}
  \label{fig:3d_temp}
\end{figure}

\subsection{Comparison with \gls{MSRE}}

\begin{figure}[htpb]
  \centering
  \includegraphics{fuel_vs_moderator_axial_sweep.eps}
        \caption{Moltres predicted axial temperature profiles near r = 0}
  \label{fig:moltres_axial_temps}
\end{figure}

\begin{figure}[htpb]
  \centering
  \includegraphics{msre_axial_temps.png}
        \caption{\gls{MSRE} design axial temperature profiles near r = 0}
  \label{fig:msre_axial_temps}
\end{figure}

\begin{figure}[htpb]
  \centering
  \includegraphics[width=\maxwidth{\textwidth}]{fast_vs_thermal_nt_flux_msre.png}
  \caption{\gls{MSRE} design radial temperature profiles at reactor mid-plane}
  \label{fig:msre_radial_temps}
\end{figure}

\subsection{Scaling study}

As described earlier, Moltres runs naturally in parallel. To test its
performance, a scaling study was conducted using a typical 2D axisymmetric input
file. Moltres's performance is shown in \cref{fig:scaling_study}. The solution
time follows very closely to the ideal; slight deviations are expected due to
the expense of communication and the nature of iterative solvers. More
parallelism means more ``older'' information is used in the solution process,
which leads to slower convergence in terms of iterations \cite{satish_balay_petsc_2015}.

\begin{figure}[htpb]
  \centering
  \includegraphics{scaling_study.eps}
  \caption{Moltres performance on a typical 2D axisymmetric problem for
    different numbers of processors}
  \label{fig:scaling_study}
\end{figure}
